---
title: "PLEAC01-01"
author: "Robert A. Stevens"
date: "November 13, 2014"
output: html_document
---

PLEAC - Programming Language Examples Alike Cookbook

1. Strings

1.1 Introduction

http://pleac.sourceforge.net/pleac_perl/strings.html

```{r, engine='perl', comment=NA}
$string = '\n';                     # two characters, \ and an n
print $string . "\n";

$string = 'Jon \'Maddog\' Orwant';  # literal single quotes
print $string;

$string = "\n";                     # a "newline" character
print $string;

$string = "Jon \"Maddog\" Orwant";  # literal double quotes
print $string . "\n";

$string = q/Jon 'Maddog' Orwant/;   # literal single quotes
print $string . "\n";

$string = q[Jon 'Maddog' Orwant];   # literal single quotes
print $string . "\n";

$string = q{Jon 'Maddog' Orwant};   # literal single quotes
print $string . "\n";

$string = q(Jon 'Maddog' Orwant);   # literal single quotes
print $string . "\n";

$string = q<Jon 'Maddog' Orwant>;   # literal single quotes
print $string . "\n";

$a = <<"EOF";
This is a multiline here document
terminated by EOF on a line by itself
EOF
print $a;
```

http://pleac.sourceforge.net/pleac_python/strings.html

```{r, engine='python', comment=NA}
mystr = "\n"   # a newline character
print mystr

mystr = r"\n"  # two characters, \ and n
print mystr

mystr = "Jon 'Maddog' Orwant"  # literal single quote inside double quotes
print mystr

mystr = 'Jon "Maddog" Orwant'  # literal double quote inside single quotes
print mystr

mystr = 'Jon \'Maddog\' Orwant'  # escaped single quote
print mystr

mystr = "Jon \"Maddog\" Orwant"  # escaped double quote
print mystr

mystr = """
This is a multiline string literal
enclosed in triple double quotes.
"""
print mystr

mystr = '''
And this is a multiline string literal
enclosed in triple single quotes.
'''
print mystr
```

http://pleac.sourceforge.net/pleac_ruby/strings.html

```{r engine='ruby', comment=NA}
string = '\n'                     # two characters, \ and an n
puts string

string = 'Jon \'Maddog\' Orwant'  # literal single quotes
puts string

string = "\n"                     # a "newline" character
puts string

string = "Jon \"Maddog\" Orwant"  # literal double quotes
puts string

string = %q/Jon 'Maddog' Orwant/  # literal single quotes
puts string

string = %q[Jon 'Maddog' Orwant]  # literal single quotes
puts string

string = %q{Jon 'Maddog' Orwant}  # literal single quotes
puts string

string = %q(Jon 'Maddog' Orwant)  # literal single quotes
puts string

string = %q<Jon 'Maddog' Orwant>  # literal single quotes
puts string

a = <<"EOF"
This is a multiline here document
terminated by EOF on a line by itself
EOF
puts a
```

http://pleac.sourceforge.net/pleac_haskell/strings.html

https://raw.githubusercontent.com/yihui/knitr-examples/master/026-engine-haskell.Rmd

Note we have to specify the compiler manually, e.g. `engine.path='ghc'` (`haskell` itself may not exist as an executable program).

{r test-haskell, engine='haskell', engine.path='ghc', cache=TRUE}
str  = "\\n"                             -- two characters, \ and an n
str2 = "Jon 'Maddog' Orwant"             -- in haskell we can do string only with ", no single quote
str3 = "\n"                              -- a "newline" character
str4 = "Jon \"Maddog\" Orwant"           -- literal double quotes
str5 = "Multiline string must use a backslash at end of line\n\
\and a backslash at beginning of line\n";
str6 = "It is a common practice\n\
       \to indent lines\n\
       \(the indentation doesn't change the value of the string)\n"

http://pleac.sourceforge.net/pleac_R/strings.html

```{r comment=NA}
string <- '\n'                    # a "newline" character 
string

string <- '\\n'                   # two characters, \ and an n
cat(string)

string <- "\n"                    # a "newline" character
string

string <- "\\n"                   # two characters, \ and an n
cat(string)

string <- "Jon 'Maddog' Orwant"   # literal single quotes
cat(string)

string <- 'Jon \'Maddog\' Orwant' # literal single quotes
cat(string)

string <- 'Jon "Maddog" Orwant'   # literal double quotes
cat(string)

string <- "Jon \"Maddog\" Orwant" # literal double quotes
cat(string)

string <- "This is a multiline string which will include a
newline character"
cat(string)

string <- paste(
  "This is also a multiline",
  " string made from",
  " concatenating a string list"
  , sep = "")
cat(string)
```
